\documentclass{beamer}
\usepackage{lipsum}
\title{Google Gemini}
\author{Harikrishna Dev}
\institute{University of Texas at Dallas}
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Overview}
  \begin{itemize}
    \item Introduction to Google Gemini
    \item Key Features
    \item Applications
    \item Future Prospects
  \end{itemize}
  
ote{This slide provides an overview of the main points we will cover in the presentation.}
\end{frame}

\begin{frame}{Introduction to Google Gemini}
  \begin{itemize}
    \item Google Gemini is a cutting-edge AI project by Google.
    \item Focuses on advanced machine learning and AI techniques.
  \end{itemize}
  
ote{Introduce the audience to Google Gemini and its significance in the AI industry.}
\end{frame}

\begin{frame}{Key Features}
  \begin{itemize}
    \item Robust Natural Language Processing (NLP) capabilities.
    \item Advanced image and video recognition.
    \item Enhanced predictive analytics.
  \end{itemize}
  
ote{Discuss the main features that make Google Gemini a powerful tool.}
\end{frame}

\begin{frame}{Applications}
  \begin{itemize}
    \item Healthcare: Improved diagnostics and personalized medicine.
    \item Finance: Better risk assessment and fraud detection.
    \item Retail: Enhanced customer experience and inventory management.
  \end{itemize}
  
ote{Explain how Google Gemini is applied in various industries to solve complex problems.}
\end{frame}

\begin{frame}{Future Prospects}
  \begin{itemize}
    \item Continued advancements in AI research.
    \item Integration with other Google services and products.
    \item Potential for widespread adoption across multiple sectors.
  \end{itemize}
  
ote{Highlight the future potential and direction of Google Gemini.}
\end{frame}

\begin{frame}{Conclusion}
  \begin{itemize}
    \item Google Gemini is a transformative AI project.
    \item Offers significant benefits across various industries.
    \item Promises continued innovation and advancements.
  \end{itemize}
  
ote{Summarize the key points and conclude the presentation.}
\end{frame}

\end{document}